---
title: "Mathematical Solutions and Python Simulations"
author: "Yu"
date: "November 13, 2017"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# System Explanations

Methods: 

1) Old: Exp(Black) = 3%; 

2) New Reset Threshold: If the 32 consecutively draws are none black, the 33th is black 

3) New Fixed Threshold: For every 33 draws, the 33th draw is black regardless the outcomes of previous draws. 

# Closed Form Solutions

## 1) Old Method

Bionomial Distribution, so $Exp = np$, and $SD = \sqrt(np(1-p))$.
```{r}
Exp = 0.03
SD = sqrt(0.03*0.97)
SD
```

## 2) New Reset Threshold

Consider the expected draws needed to get the next black is
$\sum_{1}^{32} 0.97^{i}*0.03*i + 0.97*1*33$.

```{r}
i = seq(1,32)
draws_32 = (0.97^i)*0.03*i
draws_33 = 0.97^32*1*33
```
Deeded draws are
```{r}
sum(draws_32,draws_33)
```
Thus, the expectation is 
```{r}
1/sum(draws_32,draws_33)
```

## 3) New Fixed Threshold

Suppose there are 33 draws. The first 32 draws have $Exp(black) = 0.03$, and the 33th draw's Exp is 1. The $Var = E(x^2) - E(x)$, where $E(x^2) = 32*p*(1-p+1)$ .
```{r}
Exp = ( 32*0.03 + 1 )/33
SD = sqrt( (32*0.03*(0.97+1)-Exp^2)/33 )
```
Thus, the results are 
```{r}
Exp
SD
```

## Python Simulation 
For $10^{7}$ Draws, the result is 

```{python}
import os
os.system('python draw_system_test.py')
```

